\documentclass[a4paper,12pt]{article}
\usepackage{CodeReport}

\begin{document}


\begin{center} % Everything within the center environment is centered.
	{\Large \bf Coding Report 4} % <---- Don't forget to put in the right number
	\vspace{2mm}
\end{center}  


\section{Problem Description}

In this report, we will test the execution time, error of eigen values, and error of eigen vectors
solved by power method and inverse power method.
The random matrices for testing will be symmetric diagonally dominated, defined as
$$
A = \frac{1}{2}I + B + B^{T}
$$
where $B$ is a random $50 \times 50$ matrix with entries drawn from the normal distribution.

Let $\lambda^*$ denote the largest/smallest eigen value solved by numpy as the ``ground truth'',
we measure the error of our eigen value as $\abs{\lambda - \lambda^*}$
and the error of our eigen vector as
$$
\frac{\norm{Ax - \lambda x}_{\infty}}{\lambda^*}.
$$
We will repeat each experiment 25 times and tke the average of the errors.
For each method, we will set threshold as $10 \times 10^{-4}$.

\section{Results}

\begin{table}[h]
\begin{center}
	\begin{tabular}{lrrr}
	\toprule
	{} &  lambda time &  lambda error &  Vector Error \\
	\midrule
	Smallest Eig        &     0.005557 &      0.000006 &      0.000066 \\
	Largest Eig         &     0.008837 &      0.000426 &      0.000096 \\
	Second Smallest Eig &     0.011730 &      0.000053 &      0.000057 \\
	Second Largest Eig  &     0.012146 &      0.009372 &      0.011311 \\
	\bottomrule
	\end{tabular}
	\caption{Comparison of results of power method, inverse power method, and their deflation}
\end{center}
\end{table}

From the table, we can see that both method (smallest by inverse power method and largest by power method)
uses similar amount of time.
The errors of both eigen value and eigen vector produced by inverse power method is smaller than power method.
The deflation methods to get the second largest/smallest also has similar execution time,
and both is longer than solving for largest/smallest directly.
The errors also show a similar trend that second largest's error is greater than the second smallest's for
eigen value and eigen vector.
This trend is understandable because the deflation method calls the power method or inverse power method inside.



\section{Academic Integrity}
On my personal integrity as a student and member of the UCD community, I have not given nor received any unauthorized assistance on this assignment.


\section{Appendix}

\lstinputlisting[language=Python, title=\url{numerical_methods/eigen_system.py}]{../numerical_methods/eigen_system.py}
\lstinputlisting[language=Python, title=main.py]{report4.py}

\end{document}